Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
more edits of comparison

For MySQL (Fig. \ref{fig:mysql-timeline}), we similarly validated our NFR patterns with external mailing list data. This release of MySQL was the first to be licenced under the GPL. Version 3.23.31 (January, 2001) was the production release (non-beta), and we see a flurry of topics labeled with \emph{functionality} and \emph{maintainability}, as one might expect. After this point, this version enters the maintenance phase of the lifecycle. In May 2001, there is an increase in the number of topics labelled with \emph{portability}. This might be related to release 3.23.38, which focused on Windows compatibility. Similarly, in Augsut, 2002, both \emph{functionality} and \emph{portability} are high in our tool, and mailing list data suggests this is related to the release of version 3.23.52, a general bug fix with focus on security (encoded as the \emph{functionality} NFR in the ISO9126 model). After this point, efforts shift to the newer releases (4.0, 4.1, 5.0).

@@

This analysis allows to address the questions raised in section \ref{sec:suplabelling}:

\textbf{Do label frequencies change over time?} -- In both projects the frequencies generally decreased with age. 
However, there are variations within our NFR labels. In MySQL, \emph{usability} and \emph{efficiency} do not appear very often in topics. 
A proportionately smaller number of commits addressed these NFRs.
As discussed in the section previous, certain peaks in topic numbers coincide with particular emphases in the development team, such as new releases or bug fixes.
This suggests that maintenance activity is not necessarily strictly decreasing with time, but rather episodic and responsive to outside stimuli. 
In MaxDB, we can observe that \emph{Maintainability} topics became more prevalent as MaxDB matures. This is likely due to our analysis time horizon being shorter than the MySQL product.

>>>>

For MySQL (Fig. \ref{fig:mysql-timeline}), we similarly validated our NFR patterns with external mailing list data. This release of MySQL was the first to be licenced under the GPL. Version 3.23.31 (January, 2001) was the production release (non-beta), and we see a flurry of topics labeled with \emph{functionality} and \emph{maintainability}, as one might expect. After this point, this version enters the maintenance phase of its lifecycle. In May 2001, there is an increase in the number of topics labelled with \emph{portability}. This might be related to release 3.23.38, which focused on Windows compatibility. 
Similarly, in Augsut, 2002, both \emph{functionality} and \emph{portability} are frequent, and mailing list data suggests this is related to the release of version 3.23.52, a general bug fix with a focus on security (encoded as the \emph{functionality} NFR in the ISO9126 model). 
After this point, efforts shift to the newer releases (4.0, 4.1, 5.0).

@@

This analysis allows to address the questions raised in Section \ref{sec:suplabelling}:

\textbf{Do label frequencies change over time?} -- In both projects the frequencies generally decreased with age. 
However, there are variations within our NFR labels. In MySQL, \emph{usability} and \emph{efficiency} do not appear very often in topics. 
A proportionately smaller number of commits addressed these NFRs.
As discussed in the previous section, certain peaks in topic numbers coincide with a particular emphasis from the development team on issues such as new releases or bug fixes.
This suggests that maintenance activity is not necessarily strictly decreasing with time, but rather episodic and responsive to outside stimuli. 
In MaxDB, we can observe that \emph{Maintainability} topics became more prevalent as MaxDB matures. 
This is likely due to our analysis time horizon being shorter than the MySQL product.
